<!-- README.md is generated from README.rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```


# srppp - R package to read XML dumps of the Swiss Register of Plant Protection Products

<!-- badges: start -->
[![CRAN version](https://www.r-pkg.org/badges/version/srppp)](https://cran.r-project.org/package=srppp)
[![R-universe status](https://agroscope-ch.r-universe.dev/badges/srppp)](https://agroscope-ch.r-universe.dev/srppp)
[![R-CMD-check](https://github.com/agroscope-ch/srppp/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/agroscope-ch/srppp/actions/workflows/R-CMD-check.yaml)
[![DOI](https://zenodo.org/badge/832080563.svg)](https://doi.org/10.5281/zenodo.13993340)
<!-- badges: end -->

## Description

```{r, results = "asis", echo = FALSE}
read.dcf("DESCRIPTION")[, "Description"] |> cat()
```

## Installation from CRAN

```
install.packages("srppp")
```

## Installation of the latest development code

```
install.packages("srppp",
  repos = c("https://agroscope-ch.r-universe.dev", "https://cran.r-project.org"))
```

## Documentation

A good point to start is the vignette 
["Get Started"](https://agroscope-ch.github.io/srppp/articles/srppp.html)
in the online documentation. 

## See also

You may also be interested in our
[agroscope-ch/srppphist](https://agroscope-ch.github.io/srppphist/) package containing
historical registration data starting from 2011. This package is generally updated each
year after the first publication of the register as an XML file.
