---
title: Find alternative products for all products containing a certain active substance
author: Marcel Mathis and Johannes Ranke
date: Last change 6 February 2024 (rebuilt `r Sys.Date()`)
output:
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Find alternative products for certain active substances}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = TRUE, message = FALSE}
knitr::opts_chunk$set(tidy = FALSE, cache = FALSE)
options(knitr.kable.NA = '')
library(psmv)
library(fgpsm)
library(dm)
library(dplyr)
library(knitr)
```

The current PSMV published at the FOAG website is retrieved, and the tables
relevant for the analysis are selected.

```{r psmv_current}
psmv <- psmv_dm(psmv_xml_url)
```

# Find all indications for an active substance

## Lambda-cyhalothrin

The contents of the PSMV are filtered, and only information
related to products containing lambda-cyhalothrin are kept.

```{r}
psmv_lambda <- dm_filter(psmv, 
  substances = (substance_de == "Lambda-Cyhalothrin"))
```

Currently there are 14 products, with 440 uses on 998 cultures
and 1617 pests in the PSMV:

```{r}
dm_nrow(psmv_lambda)
```

As each use can be in more than one culture, and for more than one pest,
we have a lot more use definitions when considering these separately.

```{r}
lambda_uses <- psmv_lambda$uses |>
  left_join(psmv$cultures, by = join_by(wNbr, use_nr), relationship = "many-to-many") |>
  left_join(psmv$pests, by = join_by(wNbr, use_nr), relationship = "many-to-many") |>
  left_join(psmv$application_areas, by = join_by(wNbr, use_nr), relationship = "many-to-many")
print(lambda_uses)
```

Here, we are only interested in unique combinations of cultures and pest 
organisms. 

```{r}
lambda_pests_x_cultures_x_application_areas <- lambda_uses |>
  select(culture_de, pest_de, application_area_de) |>
  unique() |>
  arrange(culture_de, pest_de, application_area_de)
print(lambda_pests_x_cultures_x_application_areas)
```

